\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{titling}

\geometry{a4paper, margin=1in}

\title{Snapshot Objectives}

\author{
	Taiten McKiver\\
	\and
	Brandon Polanco\\
	\and
	Jesse Saroca\\
	\and
	Thomas Stender
	}
	
\date{November 2025}
	
\setlength{\droptitle}{6cm}

\pagestyle{fancy}

\fancyhead[L]{Snapshot Objectives}
\fancyhead[R]{Page \thepage}
\fancyfoot[C]{}

\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}

\section*{Start Objective}
The starting objective of the Campus AR NAV will be to set up the user interface and basic backend pieces for an Android application. We will need to begin with the following:
\begin{itemize}
\item Developing a user-friendly interface on the Android mobile application.
\item Implement the Augmented Reality software.
\item Implementing a database to store locations and routes around campus.
\end{itemize}
% the whole thing is built on Android API
% Augmented Reality software is on Unity

\section*{Checkpoint 1}
The primary objective for Checkpoint 1 is to implement tracking software so that the program can identify their location. The next thing to do is to add all the classrooms' and offices' locations to the database and map out the routes and store it into the database.
% Use Routing API and RoutePlanningOptions
% location services: uses-permission android:name= "android.permission.INTERNET", "android.permission.ACCESS_COARSE_LOCATION", "android.permission.ACCESS_FINE_LOCATION"
% Checkpoint 1's testing phase will include testing the AR software on the footage.

\section*{Checkpoint 2}
The primary objective for Checkpoint 2 is to program the navigation software to show directions towards any valid location that a user will input. 

\section*{Final Checkpoint}
The primary objective for the Final Checkpoint is to clean up the user interface for readability and usability and optimize routes for accessibility and efficiency.

\end{document}