\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{titling}

\geometry{a4paper, margin=1in}

\title{Campus AR NAV\\
Software Design Document}
\author{
	Taiten McKiver\\
	\and
	Brandon Polanco\\
	\and
	Jesse Saroca\\
	\and
	Thomas Stender
	}
\date{November 2025}

\setlength{\droptitle}{6cm}

\pagestyle{fancy}
\fancyhead[L]{Campus AR NAV SDD}
\fancyhead[R]{Page \thepage}
\fancyfoot[C]{}

\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}

\thispagestyle{empty}
\tableofcontents
\newpage

\section*{Version History}
\addcontentsline{toc}{section}{Version History}
\begin{table}[ht]
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
    \textbf{User} & \textbf{Date} & \textbf{Reason for Changes} & \textbf{Version}\\
    \hline
         Jesse Saroca &  12/5/25 &  Update for snapshot 1 & 1.0 \\
    \hline
    \end{tabular}
\end{table}
\newpage

% SECTION 1
\section{Introduction}

\subsection{Purpose}
The purpose of this document is to provide a detailed description of the Campus AR NAV (CARN). This document will outline the system architecture, user interface, and intended audience for the application.

\subsection{Intended Audience}
The intended audience for this document includes:
\begin{itemize}
	\item Software Developers
	\item Project Managers
	\item Testers
	\item Stakeholders
\end{itemize}

\subsection{Overview}
The CARN will be a mobile application that allows users to use their phone camera to navigate through their college campuses. The application will provide a user-friendly interface and clear instructions that will guide the user. 
\subsection{References}
See the references section for a list of documents and resources referenced in this document.
\subsection{Definitions, Acronyms, and Abbreviations}
See the glossary section for definitions of terms, acronyms, and abbreviations used in this document.
\newpage

% SECTION 2
\section{System Architecture}
\subsection{Workflow}

\subsection{Site Breakdown}


\subsection{Architecture Overview}

\subsection{Data Flow - New Audit}

% SECTION 3
\section{User Interface}

\subsection{How to Use}

\subsubsection{Web Application}

\subsubsection{Mobile Application}

\subsection{Database Explanation}


\section*{Glossary}
\addcontentsline{toc}{section}{Glossary}
\begin{description}
    \item[\textbf{CARN}] - Campus AR NAV
    \item[\textbf{AR}] - Augmented Reality
    \item[\textbf{NAV}] - Navigation 
\end{description}
\newpage

\addcontentsline{toc}{section}{References}
\begin{thebibliography}{9}
     Ascent - Project. (2017). Cysun.org. https://ascent.cysun.org/project/project/view/72
     Ascent - Project. (2022). Cysun.org. https://ascent.cysun.org/project/project/view/44
\end{thebibliography}

\end{document}