\documentclass{article}

\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}

\geometry{a4paper, margin=1in}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{Design Specification}
\fancyfoot[C]{\thepage}

\title{Design Specification}
\author{Jesse Saroca, Thomas Stender, Brandon Polanco, Taiten McKiver}
\date{December 2025}

\begin{document}
\maketitle

\section{Overview}
EagleNav is a cross platform mobile application that provides accessible campus navigation.
The system consists of a Flutter mobile frontend, a backend API, and read only
integration with university accessibility and building data.

\section{UI/UX Pages and Components}

\begin{itemize}
    \item \textbf{Landing Page} – Start navigation, saved routes, settings.
    \item \textbf{Login/SSO Page (Optional)} – Imports schedule data.
    \item \textbf{Map Page} – Interactive map, accessibility overlay.
    \item \textbf{Route Selection Page} – Start/end selection and route options.
    \item \textbf{Turn-by-Turn Navigation} – Visual, audio, and haptic guidance.
    \item \textbf{Alerts Page} – Displays campus accessibility notifications.
    \item \textbf{Saved Routes Page} – Locally stored user shortcuts.
    \item \textbf{Settings Page} – Accessibility preferences and app controls.
\end{itemize}

\section{System Components}

\begin{itemize}
    \item \textbf{Mobile Frontend (Flutter)} – UI, map rendering, local storage.
    \item \textbf{Backend API} – Routing, alerts, building data endpoints.
    \item \textbf{University Data Services} – Accessibility + building metadata.
\end{itemize}

\section{Dependencies and Libraries}

\subsection{Frontend (Flutter)}
\begin{itemize}
    \item \texttt{flutter\_map} or \texttt{google\_maps\_flutter}
    \item \texttt{http}
    \item \texttt{provider}
    \item \texttt{shared\_preferences}
    \item \texttt{geolocator}
    \item \texttt{flutter\_tts}
\end{itemize}

\subsection{Backend}
Python:
\begin{itemize}
    \item \texttt{fastapi}, \texttt{uvicorn}, \texttt{requests}
\end{itemize}

Or Node:
\begin{itemize}
    \item \texttt{express}, \texttt{axios}, \texttt{cors}
\end{itemize}

\subsection{System Requirements}
\begin{itemize}
    \item Flutter SDK
    \item Android SDK
    \item Python 3.10 or Node.js 18+
    \item Git
\end{itemize}

\section{Docker Container Requirements}

\begin{itemize}
    \item Base image: \texttt{python:3.10} or \texttt{node:18}
    \item Install Flutter SDK + Android command line tools
    \item Install backend libraries (FastAPI or Express)
    \item System tools: \texttt{curl}, \texttt{git}, \texttt{openjdk-11-jdk}
    \item Environment variables:
    \begin{itemize}
        \item \texttt{API\_KEY}
        \item \texttt{UNIVERSITY\_DATA\_ENDPOINT}
    \end{itemize}
\end{itemize}

\section{Conclusion}
This design spec outlines the essential UI pages, major components,
dependencies, and Docker requirements needed for EagleNav to run consistently in
development or deployment environments.

\end{document}
